---
title: "Japan Multi Modal Granger Causality Test"
author: "Marvin Wen Li"
date: "2022-04-20"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

This is a vector autoregressive (VAR) model is used to assess Granger causality. The model uses multiple indicators provided by Bank of Japan. 

VAR regression involves running a series of regressions of the first-differences of a dependent variable on lagged first differences of other explanatory variables along with lagged values of the dependent variable. In each regression, a different dependent variable is used so through these series of regressions causal direction can be examined. 

## Variables

Inco = inland coastal Freight
Ocean = Ocean Freight
Rail = Railroad 
Air = Air Freight
Road = Trucking
BDI = Baltic Dry Bulk Index 

## loading library

```{r}
library(bruceR)
library(tseries)
library(rtweet)
library(vars)
library(mFilter)
library(tseries)
library(TSstudio)
library(forecast)
library(tidyverse)
library(dplyr)
library(hablar)
library(readxl)
```

## Loading data set

Data set is relatively small and has been cleaned 

```{r }
Japan_BOJ <- read_excel("/Users/marvinlee/Desktop/Research/Japan BOJ.xlsx")
View(Japan_BOJ)
```

## created time series

```{r }
INCO <- ts(Japan_BOJ[,6], start=c(1999,7), frequency = 12)
Ocean <- ts(Japan_BOJ[,3], start=c(1999,7), frequency = 12)
Rail <- ts(Japan_BOJ[,12], start=c(1999,7), frequency = 12)
Air <- ts(Japan_BOJ[,9], start=c(1999,7), frequency = 12)
BDI <- ts(Japan_BOJ[,21], start=c(1999,7), frequency = 12)
Road <- ts(Japan_BOJ[,13], start=c(1999,7), frequency = 12)
```

## Plotting

```{r }
autoplot(INCO)
autoplot(Ocean)
autoplot(Rail)
autoplot(Air)
autoplot(BDI)
autoplot(Road)
```

## stationary test level

```{r }
adf.test(log(INCO))
adf.test(log(Ocean))
adf.test(log(Rail))
adf.test(log(Air))
adf.test(log(BDI))
adf.test(log(Road))
```

## first differences

```{r }
d_lninco <- diff(log(INCO))
d_lnocean <-diff(log(Ocean))
d_lnrail <-diff(log(Rail))
d_lnair <-diff(log(Air))
d_lnbdi <-diff(log(BDI))
d_lnroad <-diff(log(Road))
```


## stationary test after first diff 

```{r }
adf.test(d_lninco)
adf.test(d_lnocean)
adf.test(d_lnrail)
adf.test(d_lnair)
adf.test(d_lnbdi)
adf.test(d_lnroad)
```

## built VAR model


```{r }
var_all <- cbind(d_lninco, d_lnocean, d_lnrail, d_lnair, d_lnbdi, d_lnroad)
```

## lag selection for all variables; AIC
```{r }
lagselect_all <- VARselect(var_all, lag.max = 15, type = "const")
lagselect_all$selection
```

## var all
```{r }
model_all <- VAR(var_all, p = 3) 
summary(model_all)
```

## Granger analysis; one to all

```{r }
granger_causality(model_all)
```



